\LARGE \bf Human-Robot Interaction: A Deliberative Architecture

### 2013-07-24 paper.tex
Added a number of fixmes + some text reorganization

\documentclass[preprint,12pt]{elsarticle}

@@

\usepackage[draft]{fixme}

\usepackage{listings}
\usepackage{alltt}
\usepackage{fancyvrb}
\usepackage{flushend} % equalize the column length on last page

@@

@@

\subsection{The typical human-robot interaction problem}\label{sec:problem}

Let us consider a robot which is supposed to achieve interactive
object manipulation, fetch and carry tasks and similar tasks in a
domestic environment. The problem we are dealing with here is the
following. Given:
\begin {itemize}
\item a joint goal, which has been previously established and agreed
  upon (through a process which is out of the scope of this paper),
\item the current situation, acquired through perception or
  deduction from previous perceptions, including the state of the
  environment of the robot and of the human,
\end {itemize}
the robot controller computes an action to execute and who (the 
human or the robot, or both in case of a joint action) has to perform
it, and then controls or monitors its execution. The operation
continues until the goal is achieved, is declared unachievable or is
abandoned by the human.

To do so, the robot has to be equipped with a number of decisional, planning
and interpretation abilities where its human partner is taken
explicitly into account. It needs to be able:
\begin {itemize}
\item to build and maintain relevant robot and human beliefs
  (from the robot perspective) with respect to state of the world and the task,
\item to build and maintain iteratively shared (human-robot) plans, 
\item to refine and execute the actions it has to perform, and to monitor 
those achieved by its human partner.
\end {itemize}

@@

Natural interaction and cooperation are on the (dare we say,
\emph{short-term}) agenda for the human-robot interaction community. They are
keys to the broad class of \emph{interactive manipulation problems}: several
agents agree on a (more or less implicit) joint goal that requires some sort of
cooperation to be successfully achieved. This class of problems involves both
dialogue and manipulation and they are often initially underspecified: they
require iterative and interactive resolution.

@@

We have chosen to tackle the challenge from several ends: human-aware
navigation and motion planning~\cite{Mainprice2011}, situation assessment
coupled with motion planning~\cite{Mainprice2012}, projection of
``mightabilities'' that anticipates what surrounding agents may
do~\cite{Pandey2011}, and the design and deployment of a pervasive
\emph{knowledge-oriented} software architecture.

The last item is the focus of this paper: what ``knowledge-oriented''
architecture means, and what its benefits and drawbacks are.

\subsection{Article overview}

In the next section, we first introduce the deliberative layer of our robots at
the functional level. It represents what we call a \emph{knowledge-oriented}
architecture, built around a central knowledge management tool called the
OpenRobot Ontology ({\sc Oro}) server.

The following sections present each of the facets of this deliberative layer:
how knowledge is produced asynchronously from geometric reasoning, how the
robot conducts grounded multi-modal interaction with humans, how knowledge is
used by decision-making components like the robot controller or the task
planner, and finally, how our knowledge-oriented architecture enables the
implementation of specific internal cognitive processes.

We conclude the article with a discussion about the strengths and weaknesses of
such a knowledge-oriented architecture.

@@

\subsection{The Psycho-Cognitive Grounds of Human-Robot Interaction}

....summary of the challenges that human-robot interaction presents to robotics.

\subsection{The LAAS deliberative layer}

@@

@@

@@

%\subsubsection*{Agents and action streams:}
\vspace{0.3cm}
\noindent
\textbf{Agents and action streams:}
The robot plans not only for itself but also for the other agents. The
resulting plan, called ``shared plan'' is a set of actions that form
a stream for each agent involved in the goal achievement. Depending on
the context, some ``shared plans'' contain causal relations between
agents. For example, the second agent needs to wait for the success of
the first agent's action to be able to start its own action. When the
plan is performed, causal links induce synchronization between
agents. Figure~\ref{plan_hatp1} illustrates a plan with two streams.

@@

%\subsubsection*{Action costs and social rules:}
\vspace{0.3cm}
\noindent
\textbf{Action costs and social rules:}
A cost and a duration function is associated to each action.
The duration function provides a duration interval for the action
achievement and is used, in one hand, to schedule the different
streams and, in the other hand, as an additional cost function.
In addition to these costs, HATP also takes into account a set of social
rules.  Social rules are constraints aiming at leading the plan
construction towards the best plan according to some human
preferences. The social rules we have defined so far deal with:

@@

%\subsubsection*{Several levels of cooperation:} 
\vspace{0.3cm}
\noindent
\textbf{Several levels of cooperation:} 
By tuning its costs
and adapting its social rules, HATP can be used to compute various
alternative plans. These plans can be categorized into several levels
of cooperation

@@

@@

Those items are not new \emph{per se}. It seems however interesting to
underline the shift of focus this implies during the design and integration
phases. The
versatility of this paradigm could be illustrated by a simple imaginary
scenario with a blind robot and a deaf robot. The blind robot does not see (no
cameras or alike), but someone can verbally describe a scene to it. On the
other hand, the deaf robot has a good vision system, but cannot process verbal
input.  Without any changes to the software architecture that we described,
control modules of both robots could equally perform the same tasks since all
the knowledge is abstracted and centralised (note that to actually implement
this imaginary situation, the blind robot would of course need \textit{a
priori} 3D models of objects talked about to enable planning or pick and place
actions, and the deaf robot would require at least some gesture interpretation
to understand orders).

>>>>

\documentclass[preprint,5p]{elsarticle}

@@

\usepackage[draft, nomargin, marginclue, footnote]{fixme}

\usepackage{listings}
\usepackage{alltt}
\usepackage{fancyvrb}

%\usepackage[bookmarks]{hyperref}

@@

\listoffixmes

@@

\subsection{The human-robot interaction challenge}\label{sec:problem}

\fxfatal{Develop/reorganize this section to organize the different problems of
HRI into one coherent challenge for AI. See how to articulate it with section
\ref{sec:psychocognitivegrounds}}

\paragraph{The Joint Action Challenge} Let us consider a robot which is
supposed to achieve interactive object manipulation, fetch and carry tasks and
similar tasks in a domestic environment. The problem we are dealing with here
is the following. Given:

\begin {itemize}
\item a joint goal, which has been previously established and agreed
  upon (through a process which is out of the scope of this paper),
\item the current situation, acquired through perception or
  deduction from previous perceptions, including the state of the
  environment of the robot and of the human,
\end {itemize}

the robot controller computes an action to execute and who (the 
human or the robot, or both in case of a joint action) has to perform
it, and then controls or monitors its execution. The operation
continues until the goal is achieved, is declared unachievable or is
abandoned by the human.

To do so, the robot has to be equipped with a number of decisional, planning
and interpretation abilities where its human partner is taken
explicitly into account. It needs to be able:

\begin {itemize}
\item to build and maintain relevant robot and human beliefs
  (from the robot perspective) with respect to state of the world and the task,
\item to build and maintain iteratively shared (human-robot) plans, 
\item to refine and execute the actions it has to perform, and to monitor 
those achieved by its human partner.
\end {itemize}

@@

The main scientific contributions of the article are summarized here, to guide
the reader. We develop and discuss them, also in relation to other works, at
the end of the article.

\fxfatal{Rewrite section 'summary of contributions'}

@@

We have chosen to tackle the challenge from several ends: human-aware
navigation and motion planning~\cite{Mainprice2011}, situation assessment
coupled with motion planning~\cite{Mainprice2012}, projection of
``mightabilities'' that anticipates what surrounding agents may
do~\cite{Pandey2011}, and the design and deployment of a pervasive
\emph{knowledge-oriented} software architecture~\cite{Lemaignan2013}.

@@

\subsection{The Psycho-Cognitive Grounds of Human-Robot Interaction}
\label{sec:psychocognitivegrounds}

\fxfatal{write section summary of the challenges that human-robot interaction presents to robotics.}

\subsection{Building the Deliberative Layer}

\fxfatal{Need to carefully introduce this section: how did we come up this this architecture?}

@@

\fxfatal{Rewrite this section to level up AI aspects (Mathieu)}

@@

\fxwarning{Give more implementation details. Why did we go for a custom NLP? (Severin)}

@@

\paragraph{Agents and action streams}
The robot plans not only for itself but also for the other agents. The
resulting plan, called ``shared plan'' is a set of actions that form
a stream for each agent involved in the goal achievement. Depending on
the context, some ``shared plans'' contain causal relations between
agents. For example, the second agent needs to wait for the success of
the first agent's action to be able to start its own action. When the
plan is performed, causal links induce synchronization between
agents. Figure~\ref{plan_hatp1} illustrates a plan with two streams.

@@

\paragraph{Action costs and social rules}
A cost and a duration function is associated to each action.
The duration function provides a duration interval for the action
achievement and is used, in one hand, to schedule the different
streams and, in the other hand, as an additional cost function.
In addition to these costs, HATP also takes into account a set of social
rules.  Social rules are constraints aiming at leading the plan
construction towards the best plan according to some human
preferences. The social rules we have defined so far deal with:

@@

\fxwarning{Relate HATP social rules to other AI techniques}

\paragraph{Several levels of cooperation} 
By tuning its costs
and adapting its social rules, HATP can be used to compute various
alternative plans. These plans can be categorized into several levels
of cooperation

@@

\fxfatal{Most of the Experiment section needs to be written}

@@

Those items are not new \emph{per se}. It seems however interesting to
underline the shift of focus this implies during the design and integration
phases.

\fxfatal{Insert here discussion of other major KRR systems for robots (Severin)}
